\documentclass{amsart}

\title{Idea Journal}
\author{Kovas Palunas}

\begin{document}
\maketitle
Note: Ideas and concepts better defined in another musing should be removed from this list

\section{Technology}
\subsection{Misc}
\begin{itemize}
\item{Dancing computer screen}
\begin{itemize}
\item{Have icons on the screen and windows move to music, maybe for an ad?}
\end{itemize}
\item{Put a computer/media player in a coconut}
\item{Put snare drum or smallish speakers on bike handlebars}
\item{Anything can be used to make a game!}
\item{Design coffee cups with temperature sensative materials}
\item{disposable (or not) coffee cup with lid that can be inverted for better pouring.  This is kinda possible now with disposable coffee cups.}
\item{Yo-yo that has a string that's one big loop going through the center of the bearing (if this is even possible...).  Otherwise do off-string with a big loop as your string.}
\item{Attachable glass crown for plastic soda bottles (for the experience of lips touching glass)}
\item{Screen that can switch between e-reader like functionality and normal functionality (adjustable refresh rate?)}
\end{itemize}
\subsection{Computers}
\begin{itemize}
\item{Make soft or differently textured keyboard keys}
\end{itemize}
\subsection{Tools/Useful Items}
\begin{itemize}
\item{Leatherman with knife on one side (butterfly style) and pliers on the other.  This would make the knife impossible to fully close, as switching sides would just change from knife to pliers, so maybe make the pliers fold up into the closed knife somehow?  Or maybe just embrace it and have a case.}
\item{Dissasemble-able dishes for easier hand washing}
\item{More easily customizable/refillable pen; make ink more availible to people as well}
\end{itemize}
\subsection{Energy}
\begin{itemize}
\item{Add something to $H_2$ gas to make it less explosive (something that takes up $O_2$ perhaps?) and more safe to use for fuel.  Could filter this out right before burning the gas?}
\end{itemize}

\section{Business}
\begin{itemize}
\item{Have a store where everything is in bulk, bring your own containers!}
\item{Have people deliver packages to each other as a kind-of secondardy job (if you're on the way to X neighborhood anyway, might as well pick up a package and make a bit of money).}
\end{itemize}

\section{Games}
\subsection{Video Games}
\begin{itemize}
\item{RTS where you play as God ``tending'' a civilization.  Not directly influencing them, but guiding their history.}
\item{Fantasy RPG in total first person (think Far Cry 2).  Could be hard to avoid exploits, like in Skyrim or Oblivion, though...}
\end{itemize}
\subsection{Specific Game Ideas}
\begin{itemize}
\item{TF2: Spy watch that drains health instead of cloak, but gives the spy another way to regen health (leech or natural regen or ???)}
\end{itemize}
\subsection{Misc}
\begin{itemize}
\item{How much money can you fit into your stomach at once?}
\end{itemize}

\section{Experiments To Do}
\begin{itemize}
\item{Place speakers on the sides of a shallow pyramid and spin the thing while playing music.  Stand at different angles to see what happens.}
\item{Play with resonance (break a glass)}
\item{Put a goPro, or something similar, on the rocket next quarter!}
\item{Put Broccoli ``pulp'' in a smoothie or juice (the flowery bits)}
\end{itemize}


\section{Science/Philosophy}
\begin{itemize}
\item{Organisms evolve with each other "in mind"}
\item{Philosophy through music? (???)}
\item{UW Ubi-Comp Lab is cool}
\end{itemize}
\subsection{Things to Learn More About}
\begin{itemize}
\item{Learn more about human hormonal cycles}
\item{2 dimensional standing waves}
\item{Does the human eardrum have a resonance frequency?}
\end{itemize}

\section{Social/Human}
\begin{itemize}
\item{Do good relationships involve {\it total} empathy?}
\item{Should we have a USA-wide competition for most "productive" cities (per capita), based on predefined criteria?}
\end{itemize}

\section{(My) Life}
\subsection{General Tips}
\begin{itemize}
\item{Take more ESS classes, actually maybe have some sort of freshman/upperclassman exchange about cool classes to take}
\item{Go to a random word in the dictionary to spark mind for idea-generation}
\item{Eat chips with chopsticks!}
\item{Money for engineering jobs in other countries?}
\end{itemize}
\subsection{Things to do}
\begin{itemize}
\item{Float Tank!}
\item{Buy drums on craigslist}
\item{Look more into architectural drawing or just drawing with mathematical shapes in general for fun}
\end{itemize}

\section{Cooking}
\begin{itemize}
\item{Kale with Feta Cheese and Lemon}
\item{Mango Key Lime Cheesecake and Hibachi Steak @ Cheesecake Factory}
\item{How to Make Chrisp Rice?}
\end{itemize}

\section{Environments/Architecture}
\subsection{General Thoughts}
\begin{itemize}
\item{Darkness is exciting}
\begin{itemize}
\item{running water too; combine both for amazement!}
\end{itemize}
\item{Look into heat pumps}
\item{Make hot tubs using waste heat from power plants!}
\end{itemize}
\subsection{Specific Houses}
\begin{itemize}
\item{Small underground one room house with glass walls.  Use mood lighting to illuminate the ``cut aways'' of the surrounding earth that have been made by the glass.  Maybe have an ant farm on one side of the house?}
\item{Tall house/apartment building with a waterfall down the exact center of it.  Could have rooms in the middle, but the water must always be there in some capacity.}
\item{One room\footnote{at least above ground} glass dome house giving full 360 degree or sky and surrounding area.  Maybe have etched in hexagons for interesting pattern and structure.  Could also let mosses and plants do their thing once it's built. }
\end{itemize}

\section{Clever Stuff}
\begin{itemize}
\item{"Eardrum Massagers"}
\item{``Sharp as a Marble''}
\item{``Equal Rice''}
\item{Dean, to the physics department. "Why do I always have to give you guys so much money, for laboratories and expensive equipment and stuff. Why couldn't you be like the math department - all they need is money for pencils, paper and waste-paper baskets. Or even better, like the philosophy department. All they need are pencils and paper." }
\end{itemize}

\section{Quotes}
\begin{quote}
"Believe those who are seeking the truth.  Doubt those who find it."  - Andrew Gide
\end{quote}
\par
\begin{quote}
"$i^2$ / Keeping it real." - Some T-Shirt
\end{quote}
\par
\begin{quote}
``Every gun that is made, every warship launched, every rocket fired signifies, in the final sense, a theft from those who hunger and are not fed, those who are cold and not clothed. This world in arms is not spending money alone. It is spending the sweat of its laborers, the genius of its scientists, the hopes of its children. This is not a way of life at all in any true sense. Under the cloud of threatening war, it is humanity hanging from a cross of iron.'' - Eisenhower
\end{quote}

\end{document}