\documentclass{amsart}

\title{The Human Mind}

\begin{document}

\maketitle

\section{Structure}

There are many parts to the human mind, all of which are locked in endless conflict to determine a final behavior.  The mind has evolved so that the victor of this conflict almost always determines the most selected for behavior.  For example, if one is in a physically vulnerable situation, the parts of the mind controlling physical movement and strategy are given more sway that those controlling abstract thought.  The consciousness is a part of this puzzle as well, and is often given less sway than one might think.  Substances like alcohol probably suppress certain parts of the mind, giving others more sway (has yet to be tested).  Hormones and other internal chemicals probably do this too, in a way developed by evolution.  
\par
When tired, the balance of the mind's parts must shift as well, in what way I still need to examine.  What is irritability?  Why does it happen?

\section{Mind's Model of the World}

(subtitle: maybe move/change this section?)
\par
Because it is so important for humans to be able to communicate with each other (see section on influence/empathy), understanding emotions and human reactions is always an important focus of the mind.  Therefore, anthropromophizing things is a habit of the mind that helps things seem clearer and (clear this up).  Ancient gods are anthropromophizations of parts of the mind!  

\section{Influence}

One mind can feel another's pain just by simulating what it sees another go through \footnote{David Eagleman science of de- and re-humanization lectures}.  This can happen with more than just pain however; one can feel many other emotions via this ``observed simulation''.  For example, great leaders \textit{inspire} others to share their passion for something.  Watching Kevin Spacy in \emph{House of Cards} makes me personally feel powerful.  The brain simulates what it sees in this way, for reasons certianly pertaining to evolution.  
\par
\textit{\textbf{The world we experience is a construct of the mind!!}} \footnote{see people who have taken LSD and a whole host of examples from Eagleman}

\section{Human Evolutionary Pressures: \emph{Why We Do Things}}

We want to survive and avoid bodily harm.  
\par
We want to mate.
\par
For everything: \textbf{\emph{We want to predict what will happen next!!}}  Uncertianty and uncomfortableness are \emph{always} hand in hand \footnote{see Vsauce video on creepyness}.  Peace is either found when things become certian, or when worrisome things don't matter anymore (and therefore the future that matters is certian).  

\section{Things to Think About}

One's perspective (which is shaped by their purpose) is exceedingly important.  Conversation is about seeing things from different perspectives, or promoting your own.  

\section{To be addressed...}

\begin{itemize}
\item Grieving
\item Sadness
\item Superiority complex
\end{itemize}

\end{document}
